\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage[colorlinks,linkcolor=black]{hyperref}

% Set margins
\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=0in
\textheight=9.25in

\raggedright

%\pagenumbering{arabic}
\thispagestyle{empty}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

% Add your personal contents from here!!! 

% Several instructions: 

% \textbf{} bold
% \emph{} or \textit{} italic type
% \underline{} underline
% %--the compiler ignores the text behind '%'
% Set font size (from small to large)
% \tiny
% \scriptsize
% \footnotesize
% \small
% \normalsize
% \large
% \Large
% \LARGE
% \huge
% 
% More information, just google that with keyword "Latex your question"


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Tianyi Geng}{(+86) 177-0130-8306}{gty12@mails.tsinghua.edu.cn}{\href{http://tianyi.world}{http://tianyi.world}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}

% -----
	\textbf{Tsinghua University}, \emph{Department of Electronic Engineering} \hfill Beijing, P.R. China \\
Bachlor of Engineering in Electronic Engineering \hfill \emph{Aug. 2012 - Jul. 2016}(expected){} \\
GPA: 9*.**/100.00\ \ \ Rank: */241\\
Concentration: Signal Processing, Data Mining. \\
\vspace{6pt}

% -----
	\textbf{Tsinghua University}, \emph{School of Economics and Management} \hfill Beijing, P.R. China \\
Bachlor in Business Administration(Second Degree) \hfill \emph{Aug. 2013 - Jul. 2016}(expected){} \\
\vspace{6pt}

% -----
<<<<<<< HEAD
	\textbf{University of Wisconsin - Madison}, \emph{College of Electrical and Computer Engineering} \hfill Madison, WI, U.S. \\
=======
	\textbf{University of Wisconsin - Madison}, \emph{College of Engineering} \hfill Madison, WI, U.S. \\
>>>>>>> 6a3a2a3a42d536ae20103189d88ff56d732f039e
	Exchange Student, International Academic Program \hfill \emph{Aug. 2014 - Dec. 2014}{} \\
GPA: 3.92/4.00\\


\end{body}

\smallskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Professional \& Personal Skills}

\begin{body}
	\vspace{14pt}
	Computer Capability: 
	\begin{itemize}
	\itemsep 0pt
	\item Skilled in C/C++, Python, MATLAB;
	\item Familiar with Hadoop, R, Java, Linux, Mac OS X;
	\item Beginner in HTML, JavaScript.
	\end{itemize}
	\smallskip
% -----
	Background in Mathematics: Familiar with calculus, linear algebra, probability and stochastic processes, discrete mathematics, algorithms.\\
	\smallskip
% -----
	Background in Electronic Engineering: Familiar with signal processing, image processing.\\
	% -----
	Language Proficiency: Fluent in English (IELTS 7.0).\\
\end{body}
\smallskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
\header{Selected Projects}

\begin{body}
	\vspace{14pt}
% -----
	Locating chain lines from beta-radiography images \hfill \emph{Sep. 2014 - Nov. 2014}
	\begin{itemize}
	\itemsep 0pt
<<<<<<< HEAD
	\item Developed an algorithm to detect chain lines reliably and precisely;
	\item Applied multiple techniques including Gaussian filtering, statistical learning to process images;
	\item Demo: \href{http://TarnumG95.github.io/chainlinedemo.html}{http://TarnumG95.github.io/chainlinedemo.html}
	\end{itemize}
	\smallskip
% -----
	Mining Sina-Weibo (Chinese Twitter) Data \hfill \emph{Feb. 2015 - Apr. 2015}
	\begin{itemize}
	\itemsep 0pt
	\item Processed TB scale Weibo data with Python;
	\item Found user behavior patterns over time, i.e. tendency to post from mobile phones recent days. 
=======
	\item Developed an algorithm to detect chain lines reliably and precisely. 
	\item Applied multiple techniques including Gaussian filtering, statistical learning to process images. 
	\item Won the second place in class competition. 
	\item Demo: \href{http://TarnumG95.github.io/chainlinedemo.html}{http://TarnumG95.github.io/chainlinedemo.html}
>>>>>>> 6a3a2a3a42d536ae20103189d88ff56d732f039e
	\end{itemize}
	\smallskip
% -----
	Future Internet techniques driven by Big-Data \hfill \emph{Mar. 2015 - Present}
	\begin{itemize}
	\itemsep 0pt
	\item Analyzed large-scale data associated with social media and carrier network on Hadoop;
	\item Expect to find user behavior patterns through data mining and therefore develop the next generation network. 
	\end{itemize}
	\smallskip

\end{body}
\smallskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}
	% -----
	Honorable Mention, 2015 Interdisciplinary Contest on Modeling \hfill{} \emph{Apr. 2015}\\
	\smallskip
	% -----
	National Scholarship(For Top 2\%), \emph{Ministry of Education, P.R. China} \hfill{} \emph{Oct. 2014}\\
	\smallskip
	% -----
	``Dec. 9th'' Scholarship(For Top 2\%), \emph{Tsinghua University} \hfill{} \emph{Oct. 2013}\\
	\smallskip

	% -----
	First-class Scholarship for Excellent Freshmen, \emph{Tsinghua University} \hfill{} \emph{Oct. 2012}\\
	\smallskip
	% -----
	Ranked No.1 in National Matriculation Test(Science), Jilin Province (1/100,000) \hfill{} \emph{Jun. 2012}
\end{body}

\smallskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Major Courses
% \header{Main Courses}

% \begin{body}
% 	\vspace{14pt}

% 	\begin{itemize} \itemsep -0pt
% 		\item Mining Massive Datasets (Stanford CS246, Coursera)
% 		\item Computer Program Design -- 98, 97 (2012 Fall \& 2013 Spring)
% 		\item Data Structure, Numerical Analysis and Algorithms -- 89 (2013 Fall)
% 		\item Probability and Stochastic Processes(1) -- 100 (2014 Spring)
% 		\item Probability and Stochastic Processes(2) -- A (UW-Madison ECE 730, 2014 Fall)
% 	\end{itemize}

% \end{body}

% \smallskip
% \smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Miscellaneous}

\begin{body}
	\vspace{14pt}
	% -----
	\textbf {Monitor, Academic Coordinator}, \emph{Class EE25, Tsinghua University} \hfill \emph{Oct. 2012 - Sept. 2014}\\
	\smallskip
<<<<<<< HEAD
	Advisory Committee of Undergraduate Curriculum,  \emph{Tsinghua University} \hfill \emph{Dec. 2014 - Present}\\
	\smallskip
	% -----
	List of coursework: \href{http://tarnumg95.github.io/course.html}{http://TarnumG95.github.io/course.html}\\
=======
	% -----
	List of coursework: \href{tarnumg95.github.io/course.html}{http://TarnumG95.github.io/course.html}\\
>>>>>>> 6a3a2a3a42d536ae20103189d88ff56d732f039e


\end{body}

\smallskip
\smallskip


\end{document}